Figure 1. Luminal Study Groups

### 2023-03-08 reports/manuscript/Figure1.Rmd
fix space in title

---
title: "Figure 1.Luminal Study Groups"
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, out_dir, ...) {
    source("../../code/knit_function.R");
    custom_knit(inputFile, "../../lab_book/Figure1/", ...)
    })
---

>>>>

---
title: "Figure 1. Luminal Study Groups"
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, out_dir, ...) {
    source("../../code/knit_function.R");
    custom_knit(inputFile, "../../lab_book/Figure1/", ...)
    })
---
